---
title: "Surgery Research Bootcamp"
author: "Chathurangi Pathiravasan"
date: "July 05, 2021"
output:
  html_document:
    code_folding: show
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
```

```{r libraries, include=FALSE}
library(knitr)
```


R Markdown cheat sheet <https://rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf>.



## Analysis of Iris Petal and Sepal Size

In this report, we will assess the correlation between **petal** and **sepal** size for different species of iris.
It will produce the following: 

* Summary statistics for each variable in the iris dataset
* Correlations
    + Between sepal length and petal length 
    + Between sepal width and petal width
* Plot of sepal length vs. petal length 

***

### Summary Statistics

#### Without kable function
```{r summary}
data(iris)
summary(iris)
```

#### With kable function
```{r summary_kable}
data(iris)
kable(summary(iris))
```

There are `r nrow(iris)` flowers in the dataset.

***

### Correlation between sepal and petal size

```{r correlations, echo=TRUE}
lcorr <- cor(iris$Sepal.Length, iris$Petal.Length)
lcorr
wcorr <- cor(iris$Sepal.Width, iris$Petal.Width)
wcorr
```

The correlation between sepal length and petal length is `r round(lcorr, 2)`  
The correlation between sepal width and petal width is `r round(wcorr, 2)`

***

### Plot of petal length vs. sepal length

```{r length_plot, echo=TRUE, fig.height=5, fig.path='Figures/', fig.width=7}
plot(iris$Sepal.Length, iris$Petal.Length,
     xlab = "Sepal Length", ylab = "Petal Length")
```

